---
title: "Research Collaboration Analytics"
output: 
  flexdashboard::flex_dashboard:
    source_code: "https://github.com/Ifeanyi55/mental-wellness-analytics/tree/main"
    favicon: bar.png
    theme:
      bg: "white"
      fg: "black" 
      primary: "blue"
      base_font:
        google: Autour One
      code_font:
        google: JetBrains Mono
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
# Install thematic and un-comment for themed static plots (i.e., ggplot2)
# thematic::thematic_rmd()
```

At A Glance {data-icon="fa-bar-chart"}
=========================================================

Column {data-width=650 .tabset}
-----------------------------------------------------------------------

### **Research Projects**

```{r}
library(tidyverse)
library(highcharter)

# read csv file
mental_wellness_df <- read.csv("mental_wellness.csv")

# projects with the most researchers
projects_with_most_researchers <- mental_wellness_df |> 
  group_by(Publication) |> 
  summarize(num_of_researchers = n()) |> 
  arrange(desc(num_of_researchers))

# top 20 pie
pie_hc <- projects_with_most_researchers[1:20,] |> 
  hchart(
    type = "pie",
    hcaes(x = Publication,y = num_of_researchers),
    name = "Number of Researchers",
    shadow = T) |> 
  hc_title(text = "<b>Top 20 Mental Wellness Projects With The Most Researchers</b>")

pie_hc

```

### **Collaborations**

```{r}
library(tidyverse)
library(highcharter)

# read csv file
mental_wellness_df <- read.csv("mental_wellness.csv")

# gauge plot of the highest number of researchers
gauge <- highchart() |> 
  hc_pane(startAngle = -90,
          endAngle = 90,
          background = list(
            shape = "arc",
            innerRadius = "60%",
            outerRadius = "100%",
            borderWidth = 5
          )) |> 
  hc_yAxis(
    labels = list(style = list(fontSize = "15px",color = "black"))
  ) |> 
  hc_colors(colors = "green") |> 
  hc_add_series(data = 100, 
                type = "solidgauge",
                name = "Number of Researchers",
                dataLabels = list(
                  useHTML = T,
                  borderWidth = 0,
                  borderColor = "black",
                  style = list(fontSize = "20px",color = "green")
                )) |> 
  hc_tooltip(enabled = T) |> 
  hc_title(text = "<b>Highest Number of Researchers Collaborating on Mental Wellness Research Project</b>")

gauge

```

### **Researchers**
```{r}
library(tidyverse)
library(highcharter)

# read csv file
mental_wellness_df <- read.csv("mental_wellness.csv")

# top 20 researchers involved in most collaboration
researcher_most_appearing <- mental_wellness_df |> 
  group_by(Authors) |> 
  summarize(Frequency = n()) |> 
  arrange(desc(Frequency))

researcher_most_appearing |> view()  

hc_bar <- researcher_most_appearing[1:20,] |> 
  hchart(
    type = "bar",
    hcaes(x = Authors,
          y = Frequency),
    shadow = T,
    name =  "Number of Collaborations",
    color = "#ff3b01"
  ) |> 
  hc_title(text = "<b>Top 20 Researchers Involved in Most Mental Wellness Research Collaborations</b>")

hc_bar

```

Column {data-width=350}
-----------------------------------------------------------------------

### **Affiliations**

```{r}
library(tidyverse)
library(highcharter)

# read csv file
mental_wellness_df <- read.csv("mental_wellness.csv")

# affiliations with most researchers
aff_with_most_researchers <- mental_wellness_df |> 
  group_by(Affiliation) |> 
  summarize(num_of_researchers = n()) |> 
  arrange(desc(num_of_researchers))

# top 20 bar
hc <- aff_with_most_researchers[1:20,] |> 
  hchart(type = "bar",
         hcaes(x = Affiliation, 
               y = num_of_researchers),
         name = "Number of Researchers",
         color = "#0174c3",
         shadow = T) |> 
  hc_title(text = "<b>Top 20 Affiliations With The Most Mental Wellness Researchers</b>")

hc

```

### **Institutions**

```{r}
library(tidyverse)
library(highcharter)

# read csv file
mental_wellness_df <- read.csv("mental_wellness.csv")

# institutions with most researchers
inst_with_most_researchers <- mental_wellness_df |> 
  group_by(Institution) |> 
  summarize(num_of_researchers = n()) |> 
  arrange(desc(num_of_researchers))


pie_hc2 <-  inst_with_most_researchers[1:20,] |>
  hchart(
    hcaes(x = Institution, y = num_of_researchers),
    type = "pie",
    name = "Number of Researchers",
    shadow = T) |>     
  hc_title(text = "<b>Institution Categories With The Most Mental Wellness Researchers</b>")

pie_hc2 

```

Narrative {.storyboard data-icon="fa-book"}
=========================================================
### **Project introduction**
In the relentless battle against mental health issues, the research community emerges as a beacon of hope, demonstrating the power of collaboration. Researchers from diverse backgrounds unite to understand and address the complexities of mental health, creating groundbreaking therapies and fostering a more compassionate approach to care. Beyond science, they work hand in hand with clinicians, caregivers, and advocates, building a network of support that reminds individuals they are not alone. Together, they illuminate a path toward hope, resilience, and a brighter future, showcasing the enduring power of human compassion in the face of an invisible adversary.

This data visualisation project aims to shed light on the collaborative efforts of researchers to find practical solutions to mental health and mental wellness issues. "Community", in the context of this project, implies a collective effort to achieve a common goal, which is to help sufferers of mental health conditions win the fight. 
This is why there are so many researchers who have collaborated on different aspects of mental wellness research as shown in the data visualisation in order to tackle this long-standing menace to happiness and a healthy state of mind.

### The **Top 20 mental wellness projects** with the most researchers

```{r}
library(tidyverse)
library(highcharter)

# read csv file
mental_wellness_df <- read.csv("mental_wellness.csv")

# projects with the most researchers
projects_with_most_researchers <- mental_wellness_df |> 
  group_by(Publication) |> 
  summarize(num_of_researchers = n()) |> 
  arrange(desc(num_of_researchers))

# top 20 pie
pie_hc <- projects_with_most_researchers[1:20,] |> 
  hchart(
    type = "pie",
    hcaes(x = Publication,y = num_of_researchers),
    name = "Number of Researchers",
    shadow = T) |> 
  hc_title(text = "<b>Top 20 Mental Wellness Projects With The Most Researchers</b>")

pie_hc

```

***
The data used in this project was scraped from [OpenAlex.org](https://openalex.org/) using keyword search. The keywords used to search for projects and the researchers between the 1st of January 2019 and the 30th of September 2023 are ***depression***, ***anxiety***, and ***ptsd***.

The pie chart in the frame shows the top 20 research projects in the data that have the most researcher collaborations. 

These are the researchers who worked together on the research project. 

As you hover over the pie chart, you will see the titles of their research and the number of collaborating researchers in the tooltip. 

Data Source: [OpenAlex.org](https://openalex.org/)

### The **highest number of researchers** collaborating on a research project {data-commentary-width=300}

```{r}
library(tidyverse)
library(highcharter)

# read csv file
mental_wellness_df <- read.csv("mental_wellness.csv")

# gauge plot of the highest number of researchers
gauge <- highchart() |> 
  hc_pane(startAngle = -90,
          endAngle = 90,
          background = list(
            shape = "arc",
            innerRadius = "60%",
            outerRadius = "100%",
            borderWidth = 5
          )) |> 
  hc_yAxis(
    labels = list(style = list(fontSize = "15px",color = "black"))
  ) |> 
  hc_colors(colors = "green") |> 
  hc_add_series(data = 100, 
                type = "solidgauge",
                name = "Number of Researchers",
                dataLabels = list(
                  useHTML = T,
                  borderWidth = 0,
                  borderColor = "black",
                  style = list(fontSize = "20px",color = "green")
                )) |> 
  hc_tooltip(enabled = T) |> 
  hc_title(text = "<b>Highest Number of Researchers Collaborating on A Mental Wellness Research Project</b>")

gauge

```

***
The gauge plot shows the highest number of researchers who collaborated on one mental wellness research project.

The title of the research that holds this distinction of having the most collaborating researcher is ***Altered white matter micro-structural organization in post-traumatic stress disorder across 3047 adults: results from the PGC-ENIGMA PTSD consortium***

Data Source: [OpenAlex.org](https://openalex.org/)

### The **Top 20 researchers** involved in most collaborations {data-commentary-width=300}

```{r}
library(tidyverse)
library(highcharter)

# read csv file
mental_wellness_df <- read.csv("mental_wellness.csv")

# top 20 researchers involved in most collaboration
researcher_most_appearing <- mental_wellness_df |> 
  group_by(Authors) |> 
  summarize(Frequency = n()) |> 
  arrange(desc(Frequency))

researcher_most_appearing |> view()  

hc_bar <- researcher_most_appearing[1:20,] |> 
  hchart(
    type = "bar",
    hcaes(x = Authors,
          y = Frequency),
    shadow = T,
    name =  "Number of Collaborations",
    color = "#ff3b01"
  ) |> 
  hc_title(text = "<b>Top 20 Researchers Involved in Most Mental Wellness Research Collaborations</b>")

hc_bar

```

***
The bar plot shows the top 20 individual researchers who have been involved in the most mental wellness research collaborations.

This implies that they have participated in more than one research effort in the data.

The researcher who holds the distinction for the most collaborations is ***Pin Cuijpers***.

Hover over the plot to see the collaborations count of the other researchers.

Data Source: [OpenAlex.org](https://openalex.org/)

### The **Top 20 affiliations** with the most mental wellness researchers {data-commentary-width=300}

```{r}
library(tidyverse)
library(highcharter)

# read csv file
mental_wellness_df <- read.csv("mental_wellness.csv")

# affiliations with most researchers
aff_with_most_researchers <- mental_wellness_df |> 
  group_by(Affiliation) |> 
  summarize(num_of_researchers = n()) |> 
  arrange(desc(num_of_researchers))

# top 20 bar
hc <- aff_with_most_researchers[1:20,] |> 
  hchart(type = "bar",
         hcaes(x = Affiliation, 
               y = num_of_researchers),
         name = "Number of Researchers",
         color = "#0174c3",
         shadow = T) |> 
  hc_title(text = "<b>Top 20 Affiliations With The Most Mental Wellness Researchers</b>")

hc

```

***
The bar plot shows the top 20 research affiliations having the most researchers who collaborated on the mental wellness research projects in the data.

The leading affiliate organization is ***King's College London***.

Data Source: [OpenAlex.org](https://openalex.org/)

### The **Institution categories** having the most mental wellness researchers {data-commentary-width=300}

```{r}
library(tidyverse)
library(highcharter)

# read csv file
mental_wellness_df <- read.csv("mental_wellness.csv")

# institutions with most researchers
inst_with_most_researchers <- mental_wellness_df |> 
  group_by(Institution) |> 
  summarize(num_of_researchers = n()) |> 
  arrange(desc(num_of_researchers))


pie_hc2 <-  inst_with_most_researchers |>
  hchart(
    hcaes(x = Institution, y = num_of_researchers),
    type = "pie",
    name = "Number of Researchers",
    shadow = T) |>     
  hc_title(text = "<b>Institution Categories With The Most Mental Wellness Researchers</b>")

pie_hc2 


```

***
The pie chart shows institution categories having the most collaborating researchers.

The top institution category is ***education***.

Data Source: [OpenAlex.org](https://openalex.org/)


